### 2020-02-11 ChapterBackground/chapterBackground.tex
Updated: Cited Chrono in Background
Updated: Lots of references and start of P2P in Background

\begin{figure}
	\centering
	\input{Figs/ExpensivePhysics.pdf_tex}
	\caption{Expensive physics.}
	\label{ExpensivePhysics}
\end{figure}

@@

\section{Scalable Non-Real Time Physics}
Scalable Non-Real Time Physics include fluid simulations, meteorological simulations and accurate physical simulations e.g. robotics, wheeled and tracked vehicle dynamics and mechatronics. An example of a Scalable Non-Real Time Physics is Project Chrono. Non-real time physics simulation work very differently from real-time, accuracy is highly favoured as opposed to the fast, plausible simulations in real-time physics. In addition high latency (10s of ms) is a small issue relative to large time-steps used in such simulations.

@@

\subsection{P2P}

@@

>>>>

\begin{figure}
	\centering
	\input{Figs/ExpensivePhysics.pdf_tex}
	\caption{Time sequence diagram of expensive physics.}
	\label{ExpensivePhysics}
\end{figure}

@@

\section{Scalable Non-Real Time Physics}
Scalable Non-Real Time Physics include fluid simulations, meteorological simulations and accurate physical simulations e.g. robotics, wheeled and tracked vehicle dynamics and mechatronics. An example of a Scalable Non-Real Time Physics is Project Chrono \cite{Chrono}. Non-real time physics simulation work very differently from real-time, accuracy is highly favoured as opposed to the fast, plausible simulations in real-time physics. In addition high latency (10s of ms) is a small issue relative to large time-steps used in such simulations.

@@

\subsection{P2P}
P2P provides scalability, but has challenges of data consistency, communication overhead and cheating. \cite{VoroGame} proposes VoroGame, which addresses these problems.

% problem of maintaining data consistency between peers but does not provide any measures of protection against cheating.

%VoroGame, work is distributed amongst clients.
%VoroGame uses Voronoi spatial partitioning to assign a region to a peer and an overlay based on a distributed hash table for data distribution.

%Unsuitable for real-time physics as latency is too high

@@

%https://aisel.aisnet.org/cgi/viewcontent.cgi?article=3672&context=cais
